---
title: "Google Analytics_R for Data Visualization"
author: "Jiuru Lyu"
date: "Jul 21, 2022"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
library("ggplot2")
library("palmerpenguins")
```

# ggplot2 First Impression

```{r}
ggplot(data=penguins) + 
  geom_point(mapping=aes(x=flipper_length_mm,y=body_mass_g))
```

1.  `ggplot(data=data_name)` tells what data frame ggplot2 should work with.
2.  The plus sign (`+`) adds a layer to the plot. ggplot2 creates plots using multiple layers.
3.  `geom_point` tells ggplot2 to use points to represent data points.
4.  `mapping=aes()` tells ggplot2 the aesthetic.

**`ggplot(data=<DATA>)+<GEOM_FUNCTION>(mapping=aes(<AESTHETIC MAPPINGS>))`**

***Example:***

```{r}
ggplot(data=penguins) + 
  geom_point(mapping=aes(x=bill_length_mm,y=bill_depth_mm))
```

# Explore Aesthetics in Analysis

Adding a new aesthetic to our previous code:

```{r}
ggplot(data=penguins) + 
  geom_point(mapping=aes(x=flipper_length_mm,y=body_mass_g,color=species))
```

```{r}
ggplot(data=penguins) + 
  geom_point(mapping=aes(x=flipper_length_mm,y=body_mass_g,color=species,shape=species,size=species))
```

```{r}
ggplot(data=penguins) + 
  geom_point(mapping=aes(x=flipper_length_mm,y=body_mass_g,alpha=species))
```

You can also add code outside the aes function. In this case, you are not mapping to the variable, but you are changing the overall plot.

```{r}
ggplot(data=penguins) + 
  geom_point(mapping=aes(x=flipper_length_mm,y=body_mass_g),color="purple")
```

## Different Types of Geom

1.  geom_point: scatter plot
2.  geom_bar: bar charts
3.  geom_line
4.  geom_smooth: a smooth line with the existing data points
5.  geom_jitter: when the data is hard to recognize, use it for better vizulization

```{r}
ggplot(data=penguins) + 
  geom_smooth(mapping=aes(x=flipper_length_mm,y=body_mass_g)) +
  geom_point(mapping=aes(x=flipper_length_mm,y=body_mass_g))
```

```{r}
ggplot(data=penguins) + 
  geom_smooth(mapping=aes(x=flipper_length_mm,y=body_mass_g,linetype=species))
```

```{r}
ggplot(data=diamonds) + 
  geom_bar(mapping=aes(x=cut,fill=cut))
```

```{r}
ggplot(data=diamonds) + 
  geom_bar(mapping=aes(x=cut,fill=clarity))
```

## Aesthetics and Facets

1.  facet_wrap: facet the plot with a single variable
2.  facet_grid: facet the plot with two variables

```{r}
ggplot(data=penguins) + 
  geom_point(mapping=aes(x=flipper_length_mm,y=body_mass_g,color=species)) + 
  facet_wrap(~species)
```

```{r}
ggplot(data=diamonds) + 
  geom_bar(mapping=aes(x=color,fill=cut)) + 
  facet_wrap(~cut)

```

```{r}
ggplot(data=penguins) + 
  geom_point(mapping=aes(x=flipper_length_mm,y=body_mass_g,color=species)) + 
  facet_grid(sex~species)

```

# Annotation on the Plot

Adding titles, subtitles, and captions to the plot:

```{r}
ggplot(data=penguins) + 
  geom_point(mapping=aes(x=flipper_length_mm,y=body_mass_g,color=species)) + 
  labs(title="Palmer Penguins: Body Mass vs. Flipper Length",subtitle="Sample of Three Penguin Species",caption="Data collected by Dr. Kristen Gorman")
```

Adding annotation to the plot:

```{r}
ggplot(data=penguins) + 
  geom_point(mapping=aes(x=flipper_length_mm,y=body_mass_g,color=species)) + 
  labs(title="Palmer Penguins: Body Mass vs. Flipper Length",subtitle="Sample of Three Penguin Species",caption="Data collected by Dr. Kristen Gorman") + 
  annotate("text",x=220,y=3500,label="The Gentoos are the largest",color="purple",fontface="bold",size=4.5)
```

You can assign your code to variables, so you do not need to type super long codes.

```{r}
p <- ggplot(data=penguins) + 
  geom_point(mapping=aes(x=flipper_length_mm,y=body_mass_g,color=species)) + 
  labs(title="Palmer Penguins: Body Mass vs. Flipper Length",subtitle="Sample of Three Penguin Species",caption="Data collected by Dr. Kristen Gorman")

p + annotate("text",x=220,y=3500,label="The Gentoos are the largest",color="purple",fontface="bold",angle=25)
```

# Save the Plots

Use ggsave("name") to save plots.
