\include{preamble}

\title{Emory University\\\textbf{QTM 220 Regression Analysis}\\ Learning Notes}
\author{Jiuru Lyu}
\date{\today}

\begin{document}
\maketitle

\tableofcontents

\newpage
\section{Descriptive Statistics and Binary Covariates}
\begin{df}{Location}
	The \textit{location} of the data is where it is. It is about approximating the data by a constant. \[Y_i\approx\mu,\quad\text{for }i=1,\dots,n\]	
\end{df}
\begin{eg}
	Different ways to summarize location: mean, median
\end{eg}
\begin{df}{Spread}
	The \textit{spread} of the data is how far it tends to be from is location. 	
\end{df}
\begin{df}{Residuals}
	Spread summarizes the size of the \textit{residuals} left over after constant approximation. We use $\hat\epsilon$ to denote residuals. \[\residual_i\coloneqq Y_i-\hat\mu.\]
\end{df}
\begin{df}{Median Absolute Deviation and Standard Deviation}
	\begin{itemize}
		\item The \textit{median absolute deviation (MAD)} is the median size of residuals.
		\item The \textit{standard deviation (sd)} is the square root of the mean squared size of residuals. 
		\begin{rmk}The standard deviation is a sort of average in which big residuals count more than smaller ones. \end{rmk}
	\end{itemize}
\end{df}
\begin{df}{Distribution}
	We use \textit{histograms} to summarize the \textit{distribution} of the data. 
\end{df}
\begin{rmk}
	Distribution of the data tells us more information than location and spread, but less than dot plot. \emph{For example, in this context, dot plot also include the identities of the individuals in addition to the number of people having salary in the range. }
\end{rmk}
\begin{df}{Binary Data}
	\textit{Binary data} only have two options, and we usually denote those two options as $1$'s and $0$'s. 	
\end{df}
\begin{cor}{}
	Hence, when drawing a dot plot, everyone falls into either of the two lines representing $1$ and $0$.
\end{cor}
\begin{thm}{Location of Binary Data}
	The median is whichever outcome is the most common, and the mean is the proportion of $1$'s in the data. 
\end{thm}
\begin{rmk}
	Hence, a histogram tells us no more information than $\hat\mu$.	
\end{rmk}
\begin{thm}{Spread of Binary Data}
	\begin{itemize}
		\item Median absolute deviation will always be $0$ in a binary case.
		\item The standard deviation is the square root of the mean squared distance from the mean, and \[\text{sd}=\sqrt{\hat\mu\qty(1-\hat\mu)}.\]
	\end{itemize}
\end{thm}
\begin{prf}
	The claim concerning MAD is trivial. \textit{Hint: there's only two possible values in the data, so median and MAD should always be the same.}\par Now, let's consider the claim on standard deviation. \begin{align*}\sd^2&=\dfrac{1}{n}\sum_{i=1}^n\qty(Y_i-\hat\mu)^2\\&=\dfrac{1}{n}\sum_{y:\qty{0,1}}\sum_{i:Y_i=y}\qty(Y_i-\hat\mu)^2\\&=\dfrac{1}{n}\qty{N_1\qty(1-\hat\mu^2)+\qty(n-N_1)\qty(0-\hat\mu^2)}&[N_1=\text{number of }1\text{'s}]\\&=\dfrac{1}{n}\qty{N_1\qty(1-2\hat\mu+\hat\mu^2)+\qty(n-N_1)\hat\mu^2}\\&=\dfrac{1}{n}\qty{N_1-2N_1\hat\mu+n\hat\mu^2}\\&=\dfrac{1}{n}\qty{n\hat\mu-2n\hat\mu\cdot\hat\mu+n\hat\mu^2}&[N_1=n\hat\mu]\\&=\dfrac{1}{n}\qty{n\hat\mu-n\hat\mu^2}\\&=\hat\mu-\hat\mu^2=\hat\mu\qty(1-\hat\mu).\end{align*} Therefore, we know \[\sd=\sqrt{\hat\mu\qty(1-\hat\mu)}.\]
\end{prf}
\begin{rmk}
	In binary data, knowing the mean $\equiv$ knowing everything else. 
\end{rmk}



\end{document}