---
title: "Introduction to Tidyverse"
author: "Jiuru Lyu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installation and Loading

```{r}
library(tidyverse)
```

THe tidyverse includes a variety amount of packages, such as dplyr for data wrangling, ggplot2 for data visualization, etc.

## Data Wrangling

We use `dplyr` for data wrangling. We load the package first. To facilitate the illustration, we will use a data set in the `gapminder`. We also load the package.

```{r}
library(dplyr)
library(gapminder)
```

Now, let's have a preview of the `gapminder` data set.

```{r}
gapminder
```

### Select Data
We can use the `glimpse()` function to take an overview of the data: 
```{r}
glimpse(gapminder)
```
After knowing different names of the columns, we can use the `select()` function.
```{r}
gapminder_selected <- gapminder %>%
  select(country, continent, year)

gapminder_selected
```

### Filter Data

To filter the data, we can use the `filter` function. In the code below, we filter the table with lines where year is 1957.

```{r}
gapminder %>%
  filter(year == 1957)
```

To find the data for China in the year of 2002, we run the following code:

```{r}
gapminder %>%
  filter(country == 'China' & year == 2002)
```

### Sorting Data

We use the `arrange` function to sort the data in ascending or descending order. In the example, we arrange the data in ascending order of the variable `lifeExp`.

```{r}
gapminder %>%
  arrange(lifeExp)
```

If we want to sort the data in descending order, we need to use the `desc()` function.

```{r}
gapminder %>%
  arrange(desc(lifeExp))
```

To combine filtering and sorting:

```{r}
gapminder %>%
  arrange(desc(pop)) %>%
  filter(year == 1957)
```

### Change a column or Create a new column

We can use the `mutate` function to change a column or to create a new column. For example, we can convert the `lifeExp` column from years to months by multiplying the original column by 12.

```{r}
gapminder %>%
  mutate(
    lifeExp = lifeExp * 12
  )
```
c
Similarly, we can also create a new column to show that change.

```{r}
gapminder %>%
  mutate(
    lifeExpMOnths = lifeExp * 12
  )
```

Now, we can combine `filter`, `arrange`, and `mutate` together.

```{r}
gapminder %>%
  filter(year == 2007) %>%
  mutate(lifeExpMonths = lifeExp * 12) %>%
  arrange(desc(lifeExpMonths))
```

### Aggregating Data
We can use the `count()` function to count the number of one value. 
```{r}
gapminder %>%
  count(continent, sort = TRUE)
```
If we set `sort=TRUE`, the `count()` will return the results in descending order. `sort` is an optional argument, and if we omit this value, R will set it to `FALSE` automatically, returning the results in ascending order. 

We can also include a third argument in count, which is the `wt` argument. This argument specifies a weight for the `count()` function. 
```{r}
gapminder %>%
  count(continent, wt = lifeExp, sort=TRUE)
```

We can combine mutating and counting together: 
```{r}
gapminder %>%
  mutate(
    gdp = gdpPercap * pop
  ) %>%
  count(continent, wt = gdp, sort=TRUE)
```


## Data Visualization
### Plotting data - very first attempt
Now, we need to load the `ggplot2` package for data visualization.
```{r}
library(ggplot2)
```
For illustration purpose, we will only focus on the `gapminder` data for the year of 1952. So now we are assign the data to a name so we can easily refer to if afterwards. 
```{r}
gapminder_1952 <- gapminder %>% filter(year == 1952)
```
Now, we are creating our very first visualization.
```{r}
ggplot(gapminder_1952, aes(x = pop, y = gdpPercap)) + 
  geom_point()
```
Here's another try:
```{r}
gapminder_1952 %>%
  ggplot(aes(x = pop, y = lifeExp)) + 
  geom_point()
```
### Plotting data in a log scale
As you can see from the previous plot, as the population value ranges widely, we consider to convert the x-axis into a log scare. Here are two ways of doing so: 
1. Using `mutate()`: 
```{r}
gapminder_1952 %>%
  mutate(pop = log(pop)) %>%
  ggplot(aes(x = pop, y = lifeExp)) + 
  geom_point()
```

2. Using `scale_x_log10()`:
```{r}
gapminder_1952 %>%
  ggplot(aes(x = pop, y = lifeExp)) + 
  geom_point() + 
  scale_x_log10()
```
No matter which method we choose, the final output looks exactly the same. 
Here's another example:
```{r}
gapminder_1952 %>%
  ggplot(aes(x = pop, y = gdpPercap)) + 
  geom_point() + 
  scale_x_log10() + scale_y_log10()
```
### Additional aesthetics
The first additional aesthetic that we can add is COLOR. In the example below, we use color to distinguish the data points for different continents. 
```{r}
gapminder_1952 %>%
  ggplot(aes(x = pop, y = lifeExp, color = continent)) + 
  geom_point() + 
  scale_x_log10()
```
Apart from adding color, we can also modify the size of the data points. Now, we are adding the size aesthetic to our plot to present different GPD per capita of a country. 
```{r}
gapminder_1952 %>%
  ggplot(aes(x = pop, y = lifeExp, color = continent, size = gdpPercap)) + 
  geom_point() + 
  scale_x_log10()
```
### Faceting
We can use faceting to create sub-graphs from the original graph. Here's an example creating sub-graphs for different continent using `facet_wrap`.
```{r}
gapminder_1952 %>%
  ggplot(aes(x = pop, y = lifeExp)) + 
  geom_point() + 
  scale_x_log10() + 
  facet_wrap(~continent)
```
Here's another example combining additional aesthetic and faceting: 
```{r}
gapminder %>%
  ggplot(aes(x = gdpPercap, y = lifeExp, color = continent, size = pop)) + 
  geom_point() + 
  scale_x_log10() + 
  facet_wrap(~year)
```
## Grouping and Summarizing
### Summarize
We can use the `summarize()` to find the median value of the data by using the `median()` function.
```{r}
medianLifeExp <- summarize(gapminder, median(lifeExp))

medianLifeExp
```
Here's another example of using the `summarize()` function.
```{r}
gapminder %>%
  filter(year == 1957) %>%
  summarize(medianLifeExp = median(lifeExp))
```
If there are more than one things you want to include in the `summarize()` function, you can separate them by using comma. 
```{r}
gapminder %>%
  filter(year == 1957) %>%
  summarize(medianLifeExp = median(lifeExp), maxGdpPercap = max(gdpPercap))
```
### Group_by
You can use the `group_by` function to group the data into groups according to your specified criteria. 
```{r}
gapminder %>%
  group_by(year) %>%
  summarize(medianLifeExp = median(lifeExp), maxGdpPercap = max(gdpPercap))
```
As always, you can combine what you have learned with the `group_by` and `summarize` function.
```{r}
gapminder %>%
  filter(year == 1957) %>%
  group_by(continent) %>%
    summarize(medianLifeExp = median(lifeExp), maxGdpPercap = max(gdpPercap))
```
You may include more than one variables in the `group_by` function.
```{r}
gapminder %>%
  group_by(continent, year) %>%
  summarize(medianLifeExp = median(lifeExp), maxGdpPercap = max(gdpPercap))
```

We can use the `top_n()` function to return the top n rows of the data frame. For example, `top_n(df, 1)` returns the first column.
```{r}
# Which country in each continent has the highest lifeExp in 1952? 
gapminder %>%
  filter(year == 1952) %>%
  select(country, continent, lifeExp) %>%
  group_by(continent) %>%
  top_n(1)
```
```{r}
# Which country in each year has the highest pop? 
gapminder %>%
  select(country, year, pop) %>%
  group_by(year) %>%
  top_n(1)
```
As always, we can combine all we have learned together: 
```{r}
gapminder %>%
  select(country, continent, year, gdpPercap) %>%
  group_by(year, continent) %>%
  summarize(total_gdpPercap = sum(gdpPercap)) %>%
  top_n(1, total_gdpPercap)
```

### Data Selection
We can use `start_with()` and `end_with()` to select columns that starts or ends with a specific text string. For example, we want to select all columns that ends with the word "work", we can write the following code: `select(end_with('word'))`.

You can use the `rename()` function to rename one or more column of the table, using the syntax `rename(new_name = old_name)` 
```{r}
gapminder %>%
  rename(population = pop)
```
When using the `select()` function, we can use `select(new_name = col_name)` to specify a new name for a column. 
```{r}
gapminder %>%
  select(country, continent, life_expactancy = lifeExp)
```

To create a new column and drop the original column, we can use the `transmute()` function: 
```{r}
gapminder %>%
  filter(year == 1952) %>%
  transmute(country, continent,lifeExp, gdp = pop * gdpPercap) %>%
  ggplot(aes(x=lifeExp, y=gdp, color=continent)) + 
  geom_point() + 
  scale_y_log10()
```


### Visualizing summarized data
We can use `ggplot2` to visualize summarized data. 
```{r}
by_year <- gapminder %>%
  group_by(year) %>%
  summarize(medianLifeExp = median(lifeExp), maxGdpPercap = max(gdpPercap))

by_year %>%
  ggplot(aes(x = year, y = medianLifeExp)) + 
  geom_point() + 
  expand_limits(y = 0)
```
This is another example: 
```{r}
by_year_continent <- gapminder %>%
  group_by(continent, year) %>%
  summarize(medianGdpPercap = median(gdpPercap))

by_year_continent %>%
  ggplot(aes(x = year, y = medianGdpPercap, color = continent)) + 
  geom_point() + 
  expand_limits(y = 0)
```
## More on Visualization
### Line
To draw a line plot, simply substitute `geom_point()` by `geom_line()`.
```{r}
by_year_2 <- gapminder %>%
  group_by(year) %>%
  summarize(medianGdpPercap = median(gdpPercap))

by_year_2 %>%
  ggplot(aes(x = year, y = medianGdpPercap)) + 
  geom_line() + 
  expand_limits(y = 0)
```
You can also create colorful line plots. 
```{r}
by_year_continent_2 <- gapminder %>%
  group_by(year, continent) %>%
  summarize(medianGdpPercap = median(gdpPercap))

by_year_continent_2 %>%
  ggplot(aes(x = year, y = medianGdpPercap, color = continent)) + 
  geom_line() + 
  expand_limits(y = 0)
```
### Bar plots
This is an example of how you can create a bar chart: 
```{r}
by_continent <- gapminder %>%
  filter(year == 1952) %>%
  group_by(continent) %>%
  summarize(medianGdpPercap = median(gdpPercap))

by_continent %>%
  ggplot(aes(x = continent, y = medianGdpPercap)) + 
  geom_col()
```
### Histograms
This is an example of how you can create a histogram using `ggplot2`:
```{r}
gapminder_1952_2 <- gapminder %>%
  filter(year == 1952) %>%
  mutate(
    pop_by_mil = pop / 1000000
  )

gapminder_1952_2 %>%
  ggplot(aes(x = pop_by_mil)) + 
  geom_histogram(bins = 50)
```
### Box plots
Here's an example of how to create a box plot:
```{r}
gapminder_1952 %>%
  ggplot(aes(x = continent, y = gdpPercap)) + 
  geom_boxplot() + 
  scale_y_log10()
```
### Adding a title to the graph
To add a title, we use the `ggtitle()` function. 
```{r}
gapminder_1952 %>%
  ggplot(aes(x = continent, y = gdpPercap)) + 
  geom_boxplot() + 
  scale_y_log10() + 
  ggtitle("Comparing GDP per capita across continents")
```




